Understanding the Landscape of Childlessness in the U.S.: A Data-Driven Exploration (1972-2022)

### 2024-03-11 outputs/paper/paper.qmd
new formatting updates
new paragraph updates

Structurally, in @sec-intro, our paper starts with a brief dissection of the nature of childlessness in America and the contributing factors. Subsequently, in @sec-data and @sec-result, we talk about the nature of the data obtained and analyze the results garnered from the data with suitable tables and charts. Next, @sec-discussion provides further insights and future areas of study. Finally, @sec-data concludes and summarizes our main findings. To complete the paper, @sec-appendix clarifies the variables within each dataset that we've used in our paper.

@@

@tbl-nochild-marital explores people's marital status and childlessness. Trends of childlessness vary with dataset. Unsurprisingly, people who are never married have the highest percentage of childlessness. However, those who are divorced, widowed and separated have fluctuating percentages of childlessness, which is understandable due to the complex emotional nature of these marital statuses.

@@

@fig-nochild-gender illustrates @tbl-nochild-sex, which explores gender differences in childlessness within the United States over a 50-year period (1972-2022). The graph utilizes line trends to depict the percentage of childless individuals categorized by gender (Male and Female).

@@

@fig-nochild-health visualizes @tbl-nochild-health, which explores health differences in childlessness within the United States over a 50-year period (1972-2022). The graph utilizes trend lines to depict the percentage of childless individuals categorized by health conditions (Excellent, Good, Fair Poor).

Overall, the graph illustrates an increase in childlessness accross all health levels and conditions approaching 2022. As mentioned, people with excellent health has the highest percentage of childlessness, having a 10.49% increase throughout the 50-year period (28.26% in 1972 to 38.75% in 2022). People with good and fair health exhibit similar rate of childlessness in 2022, at about 30%. In particular, people with fair health markedHowever, people with poor health, once having the lowest rate of childlessness (at 12.27% in 1972), now increases to 20.40% in 2022, which translates to a substantial 8.13% increase.

@@

@fig-nochild-marital illustrates @tbl-nochild-marital, which explores marital status of people who are childless over a span of 50 years in the United States (1972-2022). The graph contains trend lines of varying marital statuses-Divorced, Married, Never married, Separated and Widowed-and how each has changed over the years in terms of childbearing status.

@@

(@) RESPONDENT'S MARITAL STATUS:
- Married
- Widowed
- Divorced
- Separated
- Never married

(@) RESPONDENT'S HEALTH CONDITION:
- Excellent
- Good
- Fair
- Poor

>>>>

Structurally, in @sec-intro, our paper starts with a brief dissection of the nature of childlessness in America and the contributing factors. Subsequently, in @sec-data and @sec-result, we talk about the nature of the data obtained and analyze the results garnered from the data with suitable tables and charts. Next, @sec-discussion provides further insights and future areas of study. Finally, @sec-data concludes and summarizes our main findings. To complete the paper, @sec-appendix clarifies how each variable within each dataset is measured.

@@

@tbl-nochild-marital explores people's marital status and childlessness. Trends of childlessness vary with this dataset. Unsurprisingly, people who are never married have the highest percentage of childlessness. However, those who are divorced, widowed and separated have fluctuating percentages of childlessness, which is understandable due to the complex emotional nature of these marital statuses.

@@

@fig-nochild-gender explores gender differences in childlessness within the United States over a 50-year period (1972-2022). The graph utilizes line trends to depict the percentage of childless individuals categorized by gender (Male and Female).

@@

@fig-nochild-health explores health differences in childlessness within the United States over a 50-year period (1972-2022). The graph utilizes trend lines to depict the percentage of childless individuals categorized by health conditions (Excellent, Good, Fair Poor).

Overall, the data illustrates an increase in childlessness accross all health levels and conditions approaching 2022. As mentioned, people with excellent health has the highest percentage of childlessness, having a 10.49% increase throughout the 50-year period (28.26% in 1972 to 38.75% in 2022). People with good and fair health exhibit similar rate of childlessness in 2022, at about 30%. In particular, people with fair health markedHowever, people with poor health, once having the lowest rate of childlessness (at 12.27% in 1972), now increases to 20.40% in 2022, which translates to a substantial 8.13% increase.

@@

@fig-nochild-marital explores marital status of people who are childless over a span of 50 years in the United States (1972-2022). The graph contains trend lines of varying marital statuses-Divorced, Married, Never married, Separated and Widowed-and how each has changed over the years in terms of childbearing status.

The data demonstrates that a significant portion of people who have never married are childless. However, more and more people are reluctant to get married but still consider having children. This is observable in the childlessness percentage decrease of people who never marry, decreasing from 96.73% in 1972 to 72.53% in 2022. For people who are divorced, separated and widowed, this percentage flucatuates, displaying the complex dynamics between these relationship status and childbearing. For married people though, this childlessness percentage also decreases, from 10.51% in 1972 to 13.97% in 2022. This again demonstrates the overall decrease of childbirths due to varying factors.

@@

(@) Are you currently--married, widowed, divorced, separated, or have you never been married?:
- Married
- Widowed
- Divorced
- Separated
- Never married

(@) Would you say your own health, in general, is excellent, good, fair, or  poor?:
- Excellent
- Good
- Fair
- Poor
